Contracts for unions and intersections are hard for Nickel

### 2021-05-09 paper.tex
Some more on existing work

This straightforward solutions makes composing the Keil and Thiemann
system with other existing systems more difficult; in the words
of Williams, Morrison, and Wadler:
"(...) the monitoring semantics for contracts of intersection and union types given by Keil
and Thiemann are not uniform. (...) If uniformity helps composition, then
special cases can hinder composition."\cite{RootCauseOfBlame}

@@

Williams, Morrison, and Wadler, take a different approach on flat contracts,
they are completely forbidden in their system, explicitly to not encounter
the previously mentioned issue.
This restriction goes against what is usually expected from dynamic checks:
validation of data, and not just inclusion on types, is an expected
feature of these systems.

\todo{Monitoring sound problem}

@@

\texttt{(define/contract overload
(and/c (-> number? number?)
       (-> string? string?))
(λ (x) x))}

>>>>

This straightforward solutions makes composing the Keil and Thiemann
system with other existing systems more difficult; in the words
of Williams, Morris, and Wadler:
"(...) the monitoring semantics for contracts of intersection and union types given by Keil
and Thiemann are not uniform. (...) If uniformity helps composition, then
special cases can hinder composition."\cite{RootCauseOfBlame}

@@

Williams, Morris, and Wadler, take a different approach on flat contracts,
they are completely forbidden in their system, explicitly to not encounter
the previously mentioned issue.
This restriction goes against what is usually expected from dynamic checks:
validation of data, and not just inclusion on types, is an expected
feature of contracts.

On top of that, a fundamental problem arises on said paper,
symptom of the difficulty of establishing good enough, and yet
simple semantics for union and intersection dynamic checks.
One of their main results, is the fact that their calculus, obeys
all of their expected monitoring properties for higher ordered, union
and, intersection contracts.
However, one of these properties states the following:

$$ K \in \llbracket A \cap B \rrbracket ~ if ~ K \in \llbracket A \rrbracket \lor K \in \llbracket B \rrbracket $$

Which means that a continuation ($K$) complies negatively with an
intersection of $A$ and $B$ if it complies with at least one of these.
Altough this is true, it's a weaker statement of what we'd like to have,
since it rules out continuations like $(\lambda f.~(K_1[f],~K_2[f])) \square$, 
where $K_1 \in \llbracket A \rrbracket$ but $K_1 \not \in \llbracket B \rrbracket$,
and dually for $K_2$, which would mean the continuation presented above would not
be in $\llbracket A \cap B \rrbracket$, even though our intuition (and the
introduction to the paper) indicates that it should.

While this mistake does not invalidate their work (the system they present
handles these correctly), it shows that existing research is still not on
good shape to handle the growing usecases being developed for
union and intersection around dynamic languages.

% $$ K ::= Id | K \bullet \square N | K \bullet V \square | K \bullet \square @^pA  $$

% Keil and Thiemann did noticed this problem, and their contract satisfaction
% rules only apply to elimination context, a particular kind of context
% where the hole is either being applied to an argument
% ($\square N$) or is used as an argument for a primitive
% operation ($O(\overrightarrow{\text{V}}, \square, \overrightarrow{\text{N}})$).

% K ::= Id | K ◦ □ N | K ◦ V □ | K ◦ □ @pA
\unsure{Is this worth mentioning? Should we go so techincal?}

@@

\texttt{(define/contract overload
(and/c (-> number? number?)
       (-> string? string?))
($\lambda$ (x) x))}
